---
title: "ደ/ብርሃን ቅ/ሥላሴ ዳላስ ቴክሳስ"
format: 
  dashboard:
    orientation: columns
    fig-width: 10
    fig-asp: 0.3
    expandable: false
brand:
  light: brand/light.yml
  dark: brand/dark.yml
editor_options: 
  chunk_output_type: console
---

```{=html}
<head>
      <style>
        nav.navbar.navbar-expand-md.slim {
          display: none;
        }
      </style>
    </head>
```



```{=html}
<!-- <link href="https://cdnjs.cloudflare.com/ajax/libs/bootstrap/5.3.0/css/bootstrap.min.css" rel="stylesheet"> -->
<link href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/6.4.0/css/all.min.css" rel="stylesheet">

<style>

.info-btn {
  /* background: none;  <-- REMOVE OR COMMENT OUT THIS LINE */
 /* background-color: #ffffff;  Add this line to make the outer circle white */
  border: none;
  /*color: #6c757d;  This is the color of the 'i' icon and its inner circle */
  font-size: 1.2rem;
  padding: 0.5rem; /* This padding creates the size of the white circle */
  border-radius: 40%;
  transition: all 0.3s ease;
  position: fixed;
  top: 15px;
  right: 20px;
  z-index: 1050;
  
  background-color: #7e8f9e;
  border: none;
  color: #292a33;
}

.info-btn:hover {
    background-color: #e9ecef;
    color: #495057;
    transform: scale(1.1);
}

.info-btn .fas { /* Target the Font Awesome icon directly */
  /* vertical-align: middle; */ /* Try this first */
  /* If 'middle' isn't enough, you might need a slight adjustment */
  vertical-align: -3px;  /* Example: push down by 2 pixels */
}
.modal-header {
    background-color: #f8f9fa;
    border-bottom: 2px solid #dee2e6;
}

.modal-title {
    color: #2c3e50;
    font-weight: 600;
}

.section-title {
    color: #495057;
    font-weight: 600;
    margin-top: 1rem;
    margin-bottom: 0.5rem;
    border-bottom: 1px solid #dee2e6;
    padding-bottom: 0.25rem;
}

.citation-text {
    background-color: #f8f9fa;
    padding: 0.75rem;
    border-left: 4px solid #007bff;
    font-family: 'Courier New', monospace;
    font-size: 0.9rem;
}
</style>

<!-- Info Button -->
<button id="infoBtn" class="info-btn" type="button" data-bs-toggle="modal" data-bs-target="#infoModal" title="About This Dashboard">
    <i class="fas fa-info-circle"></i>
</button>

<!-- Info Modal -->
<div class="modal fade" id="infoModal" tabindex="-1" aria-labelledby="infoModalLabel" aria-hidden="true">
    <div class="modal-dialog modal-lg">
        <div class="modal-content">
            <div class="modal-header">
                <h5 class="modal-title" id="infoModalLabel">
                    <i class="fas fa-info-circle me-2"></i>
                    About This Dashboard
                </h5>
                <button type="button" class="btn-close" data-bs-dismiss="modal" aria-label="Close"></button>
            </div>
            <div class="modal-body">
                <div class="section-title">
                    <i class="fas fa-calendar-alt me-2"></i>Data Period
                </div>
                <p class="mb-3">Weekly update: Monday 1:00 pm CST</p>
                
                <div class="section-title">
                    <i class="fas fa-database me-2"></i>Data Source
                </div>
                <p class="mb-2">Data originally from:</p>
                <p class="mb-2">
                    The core of its functionality relies on the Google YouTube Data API and Google YouTube Analytics API.
                    <br>

                </p>
                <p class="mb-3">
                    Accessed via: 
                    <a href="https://developers.google.com/youtube/v3" target="_blank" class="text-decoration-none">
                        <i class="fas fa-external-link-alt me-1"></i>
                        Google YouTube Data API
                    </a>
                </p>
                
                <div class="section-title">
                    <i class="fas fa-quote-left me-2"></i>Citation
                </div>
                <p class="mb-2">To cite this dashboard:</p>
                <div class="citation-text">
                    Zeleke,Y.(2026). Debre Berhan Holy Trinity EOTC Dallas-TX Dashboard [github.io]. 
                    <a href="https://github.com/yihun/eotc-youtube-channels" target="_blank" class="text-decoration-none">
                        https://github.com/yihun/eotc-youtube-channels
                    </a>
                </div>
                <div class="section-title mt-4">
                    <i class="fas fa-handshake me-2"></i>Affilations
                </div>
                <p class="mb-0">
                    This dashboard doesn't have any affilation with Debre Berhan Kidist Selassie Church of Garland TX
                </p>
                <div class="section-title mt-4">
                    <i class="fas fa-user-circle me-2"></i>Credits
                </div>
                <p class="mb-0">
                    <strong>Designed by:</strong> Yihun Zeleke, 2026
                </p>
            </div>
            <div class="modal-footer">
                <button type="button" class="btn btn-secondary" data-bs-dismiss="modal">
                    <i class="fas fa-times me-2"></i>Close
                </button>
            </div>
        </div>
    </div>
</div>

<script src="https://cdnjs.cloudflare.com/ajax/libs/bootstrap/5.3.0/js/bootstrap.bundle.min.js"></script>
```


## Column - Top 21 videos width="55%"

```{r}
#| context: setup
#| label: load-libraries
#| echo: false
#| message: false
#| inlcude: false

library(dplyr)
library(ggplot2)
library(gt)
library(lubridate)
library(stringr)
source(here::here("scripts/data_cleaning_001.R"))
source(here::here("scripts/theme_and_function.R"))

```

```{r}
#| label: top-vides
#| expandable: false
#| html-table-processing: none

generate_svg_circle <- function(views_values) {
  views_numeric <- as.numeric(views_values)
  views_numeric[views_numeric <= 0] <- 1 # prevent log(0)

  # Logarithmic scaling to smooth visual difference
  log_views <- log10(views_numeric)
  log_min <- min(log_views, na.rm = TRUE)
  log_max <- max(log_views, na.rm = TRUE)

  # Normalize radius between 16 and 40
  radius_min <- 15 # 16
  radius_max <- 30 # 40
  norm_log_views <- (log_views - log_min) / (log_max - log_min)
  radius <- radius_min + (radius_max - radius_min) * norm_log_views
  radius <- round(radius) # ensure integer radius for clean SVGs

  # Color mapping
  popularity_scaled <- round(norm_log_views * 100)
  circle_colour_picker <- colorRampPalette(c(
    "#B91d1d",
    "#ED8E11",
    "#EDDE11",
    "#1DB954",
    "#260054"
  ))
  colors <- circle_colour_picker(101)[pmin(popularity_scaled, 100) + 1]

  # Label formatting
  label_formatter <- function(x) {
    if (x >= 1e6) {
      sprintf("%.1fM", x / 1e6)
    } else if (x >= 1e3) {
      sprintf("%.1fK", x / 1e3)
    } else {
      as.character(x)
    }
  }
  labels <- vapply(views_numeric, label_formatter, character(1))

  # Tooltip exact values
  tooltip_formatter <- function(x) format(x, big.mark = ",", scientific = FALSE)
  tooltips <- vapply(views_numeric, tooltip_formatter, character(1))

  # Generate SVGs
  svg_code <- mapply(
    function(r, col, label, tip) {
      size <- 2 * r + 1 # +1 to avoid clipping on edge
      font_size <- max(5, round(r * 0.45)) # 8=>5
      label_display <- if (r < 18) "" else label

      sprintf(
        '<svg width="%d" height="%d" viewBox="0 0 %d %d" xmlns="http://www.w3.org/2000/svg" shape-rendering="geometricPrecision">
         <title>%s views</title>
         <circle cx="%d" cy="%d" r="%d" fill="%s" />
         <text x="%d" y="%d" font-size="%d" fill="white" text-anchor="middle" dy=".3em">%s</text>
       </svg>',
        size,
        size,
        size,
        size,
        tip,
        r,
        r,
        r,
        col,
        r,
        r,
        font_size,
        label_display
      )
    },
    radius,
    colors,
    labels,
    tooltips,
    SIMPLIFY = FALSE
  )

  return(svg_code)
}

clock_icon = html(
  '<svg xmlns="http://www.w3.org/2000/svg" x="0px" y="0px" width="18" height="18" viewBox="0,0,255.998,255.998"><g fill="#ffffff" fill-rule="nonzero" stroke="none" stroke-width="1" stroke-linecap="butt" stroke-linejoin="miter" stroke-miterlimit="10" stroke-dasharray="" stroke-dashoffset="0" font-family="none" font-weight="none" font-size="none" text-anchor="none" style="mix-blend-mode: normal"><g transform="scale(10.66667,10.66667)"><path d="M12,2c-5.523,0 -10,4.477 -10,10c0,5.523 4.477,10 10,10c5.523,0 10,-4.477 10,-10c0,-5.523 -4.477,-10 -10,-10zM14.586,16l-3.293,-3.293c-0.188,-0.188 -0.293,-0.442 -0.293,-0.707v-5c0,-0.552 0.448,-1 1,-1v0c0.552,0 1,0.448 1,1v4.586l3,3c0.39,0.39 0.39,1.024 0,1.414v0c-0.39,0.39 -1.024,0.39 -1.414,0z"></path></g></g></svg>'
)

# Create the gt table with custom formatting
# https://www.youtube.com/watch?v=yiS7SpT9pVc
videos |>
  mutate(views = as.numeric(views)) |>
  slice_max(order_by = views, n = 21) |>
  ungroup() |>
  arrange(desc(views)) |>
  mutate(published_at = format(as.Date(published_at), "%m-%d-%Y")) |>
  select(thumbnail_url, title, published_at, duration_sec, views) |>
  gt(id = "custom") |>
  cols_label(
    title = md("Service Type"),
    published_at = md("**Service Date**"),
    views = md("**Views**"),
    duration_sec = clock_icon,
    thumbnail_url = ""
  ) |>

  text_transform(
    locations = cells_body(columns = thumbnail_url),
    fn = function(url) {
      video_id <- videos$video_id[which(videos$thumbnail_url == url)]

      # Create YouTube video URL
      youtube_url <- paste0("https://www.youtube.com/watch?v=", video_id)

      # Create circular image with hyperlink to YouTube video
      paste0(
        "<a href='",
        youtube_url,
        "' target='_blank'>",
        "<img src='",
        url,
        "' style='border-radius:50%; height:50px; width:50px;'/>",
        "</a>"
      )
    }
  ) |>
  text_transform(
    fn = function(x) {
      generate_svg_circle(x)
    },
    locations = cells_body(columns = views)
  ) |>
  fmt(
    columns = duration_sec,
    fns = function(seconds) {
      h <- seconds %/% 3600
      m <- (seconds %% 3600) %/% 60
      s <- seconds %% 60
      sprintf("%02d:%02d:%02d", h, m, s)
    }
  ) |>
  cols_align(
    align = "center",
    columns = c(views)
  ) |>
  cols_width(published_at ~ px(100)) |>
  tab_options(
    table.font.color = "#FFFFFF",
    table.background.color = "#191414",
    table.font.size = px(12),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent",
    footnotes.background.color = "#282828",
    source_notes.background.color = "#282828",
    table.border.top.style = "hidden",
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  tab_header(
    title = html(
      "<strong style='color:grey;'>EOTC Debre Berhan (ደብረ ብርሃን):</strong> <span style='color:green;font-style: italic;'>21 most wathed videos</span>"
    )
  ) |>
  opt_css(
    css = "
  table tr:nth-child(odd) {
    background-color: #282828;
  }
    
  table tr:hover {
    background-color: #383838;
  }
  
  .cell-output-display {
    overflow: visible !important;
  }
  
  div#custom {
    overflow: visible !important;
  }

  #custom .gt_heading {
    position: sticky !important;
    top: -20px !important;
    z-index: 102 !important;
    background-color: #191414 !important;
  }

  #custom thead tr {
    position: sticky !important;
    top: -1px !important;   /* adjust this to match the exact height of your title */
    z-index: 101 !important;
  }

  #custom thead tr th {
    background-color: #191414 !important;
    border-top: none !important;
  }
  #custom table {
    border-collapse: collapse !important;
  }
  "
  )


```

## Column - Last six months videos {width="45%"}

```{r}
#| echo: false
#| include: false

six_months_videos <- videos |>
  select(-title) |>
  mutate(published = lubridate::as_date(published_at), .keep = "unused")

# Find the most recent date in the data

max_date <- max(six_months_videos$published, na.rm = TRUE)

# Filter for the last 24 weeks from that max date
six_months_videos <- six_months_videos %>%
  filter(published >= (max_date - lubridate::weeks(24)))

```

```{r, sendtoojs}
#| echo: false
#| include: false
ojs_define(six_months_videos_ojs = six_months_videos)

```

## Row - Videos: Last 6 months videos {height ="15%"}

```{ojs}

//| title: Last 6 months  videos 
//| expandable: false

// Tranpose the data to  make it usable in ojs
ojs_df_six_months = transpose(six_months_videos_ojs)

// Create a dropdown menu of the songs
viewof songDropdown = Inputs.select(
  ojs_df_six_months.map(d => d.service_clean),
  {
    label: "አዳዲስ ስብከትና ትምህርቶችን ይመልከቱ\nLatest Services and Liturgy",
    unique: true
  }
)

```

### Row - iFrame: YouTube Channel {height="40%"}

```{ojs}
//| expandable: false
html`
<iframe 
  style="border-radius:12px; display:block; margin:auto;" 
  width="100%" 
  height="200"  
  src="https://www.youtube.com/embed/${ojs_df_six_months.find(video => video.service_clean === songDropdown).video_id}" 
  title="YouTube video player" 
  frameborder="0" 
  allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" 
  referrerpolicy="strict-origin-when-cross-origin" 
  allowfullscreen 
  loading="lazy">
</iframe>
`
```

### Row - Methodods {height="45%"}

::: {#myaboutpage style="background-color:#1b0d2bff !important; border-radius:8px; color:white; !important"}
<br><br>

- This open-source YouTube analytics dashboard was developed for *EOTC Debre Berhan (ደብረ ብርሃን)* community church to provide clear, data-driven insights into channel performance and audience engagement. 
- The project integrates the YouTube Data API to collect channel and video-level metrics through a Python-based data pipeline. 
- `Postgres` + `NeoDB` is used for structured storage, transformation, and ETL processes, ensuring reliable and efficient data management.
-  The interactive dashboard is built in R, presenting growth trends, engagement rates, and content performance in an accessible and actionable format. 
-  Hosted on GitHub, the repository includes automated weekly data refreshes powered by GitHub Actions, enabling the dashboard to remain up-to-date without manual intervention.
- > Check out the project on Github: <a href="https://github.com/yihun/eotc-youtube-channels" target="_blank" rel="noopener noreferrer">
  https://github.com/yihun/eotc-youtube-channels
</a>

:::